### 2020-01-11 Paper_EV/Paper_EV.tex
/Paper_EV: refactoring of the actual state of the Chapter 2

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% Compile Template in following order:
%
% pdflatex Paper_EV
% makeindex Paper_EV.nlo -s nomencl.ist -o Paper_EV.nls (Table of Symbols)
% makeindex Paper_EV.acn -s Paper_EV.ist -t Paper_EV.alg -o Paper_EV.acr (Table of Acronyms)
% makeindex Paper_EV.glo -s Paper_EV.ist -t Paper_EV.glg -o Paper_EV.gls
% pdflatex Paper_EV
% pdflatex Paper_EV
%
% TODO:
% - Title page: Dr. -> Dr. ir.
%
%#################################################################################
%#################################################################################
%#################################################################################

@@

% Package for acronyms
\usepackage[acronym, automake, nopostdot, nogroupskip]{glossaries}
\setlength{\LTleft}{-0.15cm}			% left justified
\renewcommand*{\arraystretch}{1.4}		% vertical distance between entries, default is 1
% List
\newacronym{INDI}{INDI}{Incremental Nonlinear Dynamic Inversion}
\newacronym{NED}{NED}{North East Down}
\newacronym{NDI}{NDI}{Nonlinear Dynamic Inversion}
% Make gls
\renewcommand*\entryname{Acronym}
\makeglossaries

@@

...

@@

In this section general equations of motion of an aircraft are presented.

For the derivation of the equation of motion the aircraft system will be assumed to be a rigid body. Such a rigid body system can be described uniquely by 12 states. Note that by taking in account additional effects, such propulsion system dynamics, multi-body dynamics etc., the number of required state variables will increase.

Additionally to the rigid body assumption, it is also assumed that the earth is flat and non-rotating and the reference point of the force vector corresponds to the center of gravity of the body. Thus, the linear momentum equation is written as
\begin{equation}
	\begin{split}
		\sum (\bm{F}^G)_B = m \cdot \Big[ (\bm{\dot{v}}^G)_{B} + (\bm{\omega}^{OB})\times(\bm{v}^R)_{B} \Big]
		\label{eq:lin_momentum}
	\end{split}
\end{equation}
where $\sum(\bm{F}^G)_B \in \mathbb{R}^{3 \times 1}$ is the sum of the external forces acting on the system and applied to the center of gravity $G$, $m$ the mass of the body, $(\bm{\dot{v}}^G)_{B} \in \mathbb{R}^{3 \times 1}$ the linear acceleration of the point $G$, $(\bm{\omega}^{OB}) \in \mathbb{R}^{3 \times 1}$ the angular velocity of the body-fixed frame ($B$) with respect to the \acrfull{NED} ($O$) coordinate frame. Subscript $B$ denotes that all variables are specified in the body-fixed coordinate frame.

The rotational motion of a body is described with the angular momentum. To derive it, additionally to the assumptions made above it is also considered that the mass and the mass distribution are quasistationary, meaning $\frac{d}{dt}m=0$ and $\frac{d}{dt}(I)_B=0$ respectively?. $(I)_B$ is the inertia tensor of the body defined in the body-fixed frame. Thus, the angular momentum is
\begin{equation}
	\begin{split}
		\sum (\bm{M}^G)_B = (\bm{I}^G)_B \cdot (\bm{\dot{\omega}}^{OB}) + (\bm{\omega}^{OB}) \times \Big[(\bm{I}^G)_B \cdot (\bm{\omega}^{OB})\Big]
		\label{eq:ang_momentum}
	\end{split}
\end{equation}
where $\sum (\bm{M}^G)_B \in \mathbb{R}^{3 \times 1}$ is the sum of the external moments acting on the system around the center of gravity $G$,

The remaining two equations, that are necessary to fully describe the rigid body are the attitude differential equation and the position differential equation. The attitude differential equation describes the relationship between angular rates $p, q, r$ and derivatives of the Euler angles $\dot{\Phi}, \dot{\Theta}, \dot{\Psi}$ leading to
\begin{equation}
	\begin{bmatrix}
		\dot{\Phi}\\
		\dot{\Theta}\\
		\dot{\Psi}
	\end{bmatrix} =
	\begin{bmatrix}
    	1 & \sin\Phi\tan\Theta & \cos\Phi\tan\Theta \\
    	0 & \cos\Phi & -\sin\Phi \\
    	0 & \frac{\sin\Phi}{\cos\Theta} & \frac{\cos\Phi}{\cos\Theta}
    \end{bmatrix}_B
    \begin{bmatrix}
		p\\
		q\\
		r
	\end{bmatrix}_B
	\label{eq:attitude_diff_eq}
\end{equation}

@@

The above presented Equations (\ref{eq:lin_momentum})-(\ref{eq:position_diff_eq}) can be used to represent a motion of a general aircraft. $\sum(\bm{F}^G)_B$ and $\sum (\bm{M}^G)_B$ are sums of the external forces and moments acting on the aircraft. These could be the aerodynamic forces and moments caused by the air flow, propulsion forces and moments, forces caused by the gravitation etc.. The detailed modelling of external forces and moments is presented in chapter (...Simulink).

@@

In this subsection, the \acrfull{NDI} method is explained. The \acrshort{NDI} approach is based on feedback linearization and is also called \textit{Input-Output Linearization}. Often, such type of controllers is involved in tracking control tasks, where objective is to track some desired trajectory \cite{Slotine}. To derive it, consider the following nonlinear system
\begin{subequations}
	\begin{align}
		&\bm{\dot{x}} = \bm{f(x)} + \bm{G(x)}\bm{u} \label{eq:nonlin_sys1} \\
		&\bm{y} = \bm{h(x)} \label{eq:nonlin_sys2}
	\end{align}
	\label{eq:nonlin_sys}
\end{subequations}
where $\bm{x} \in \mathbb{R}^{n \times 1}$ is the state vector, $\bm{u} \in \mathbb{R}^{m \times 1}$ the input vector, $\bm{y} \in \mathbb{R}^{m \times 1}$ the system vector, $\bm{f(x)} \in \mathbb{R}^{n \times 1}$ and $\bm{h(x) \in \mathbb{R}^{m \times 1}}$ nonlinear vector fields and $\bm{G} \in \mathbb{R}^{m \times n}$ an input matrix. Note that the system presented in Equations (\ref{eq:nonlin_sys}) is affine in the input, which is not allways fulfilled. Using a state transformation $\bm{z = \phi(x)}$, the affine system from Equation \ref{eq:nonlin_sys1} can be transformed into normal (canonical) representation.

@@

In the example provided above the input-output relationsip was found after the first differentiation of the output $\bm{y}$. But if after the first differentiation the term $L_{\bm{G}}\bm{h(x)}$ is zero, output $\bm{y}$ has to be differentiated until the Lie derivative with respect to $\bm{G}$ is nonzero. The $i$-th derivative of the output is then
\begin{equation}
	\begin{split}
		\frac{\partial^i\bm{y}}{\partial t} = \frac{\partial^i\bm{h(x)}}{\partial t} = L_{\bm{f}}^i \bm{h(x)} + L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x) u}
		\label{eq:dy_i}
	\end{split}
\end{equation}
with $i$ being the \textit{relative degree} of the system. Using Equation (\ref{eq:dy_i}) to formulate the control law, leads to the following expression for the control input $\bm{u}$
\begin{equation}
	\begin{split}
		\bm{u} = L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x)}^{-1} (\bm{\nu} - L_{\bm{f}}^i\bm{h(x)}) 
		\label{eq:u_control_law_i}
	\end{split}
\end{equation}
Thus, Equation (\ref{eq:u_control_law_i}) applied to Equation (\ref{eq:dy_i}) yields the simple linear relation
\begin{equation}
	\begin{split}
		\bm{y}^i = \bm{\nu}
		\label{eq:u_control_law_i}
	\end{split}
\end{equation}
Despite wide usage (especially in the past of the flight control) of the \acrshort{NDI} method and its numerrous extensions (cite-tag Horn), it also has drawbacks.

The \acrshort{NDI} method was widely adopted for civil and military aircrafts and has numerous of extensions \cite{Horn}. Nevertheless, it has some drawbacks. The major one is that the control law derived using the \acrshort{NDI} approach is dependent on the full system dynamics model \cite{Sieberling}. As shown in the previous chapter (cite-tag prev-chapter), the equations of motion of an aircraft usually have a complicated nonlinear character. Thus, describing complex physical phenomena often leads to the inconsistency between the real aircraft and its mathematical representation used in the model. As some of those inconsistencies are inevitable there is a need to build a control law which performance is less dependent on the uncertainties of the model. This method is called \acrfull{INDI} and will be discussed in the next section.

@@

The incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
\begin{equation}
	\begin{split}
		\bm{\dot{x}} &= \bm{f(x_0)} + \bm{G(x_0)}\bm{u_0} \\
		&+ \frac{\partial}{\partial \bm{x}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{x-x_0}) \\
		&+ \frac{\partial}{\partial \bm{u}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{u-u_0}) 
		\label{eq:nonlin_sys_taylor}
	\end{split}
\end{equation}
The first term on the right side of the Equation \ref{eq:nonlin_sys_taylor} is $\bm{\dot{x}_0}$. Also, evaluating the differentiation of the third term leads to 
\begin{equation}
	\begin{split}
		\bm{\dot{x}} &= \bm{\dot{x}_0} \\ 
		&+ \frac{\partial}{\partial \bm{x}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{x-x_0}) \\
		&+ \bm{G(x_0)} (\bm{u-u_0}) 
		\label{eq:nonlin_sys_taylor2}
	\end{split}
\end{equation}
The second term of the Equation \ref{eq:nonlin_sys_taylor2} contains partial derivative with respect to the state vector. Considering very small time increments of the controller loop and applying the \textit{principle of time scale separation} the second term vanishes. This is a valid assumption if the dynamics of the actuators is fast compared with the dynamics of the system. Thus, the Equation \ref{eq:nonlin_sys_taylor2} is further simplified to 
\begin{equation}
	\begin{split}
		\bm{\dot{x}} = \bm{\dot{x}_0} + \bm{G(x_0)} (\bm{u-u_0}) 
		\label{eq:nonlin_sys_indi}
	\end{split}
\end{equation}
Solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\dot{\bm{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law can be obtained
\begin{equation}
	\begin{split}
		\bm{u} = \bm{u_0} + \bm{G(x_0)^{-1}} (\bm{\nu} - \bm{\dot{x}_0})
		\label{eq:u_control_law_indi}
	\end{split}
\end{equation}
where $\bm{\dot{x}_0}$ is a measurable value from the previous step, $\bm{u_0}$ the control input from the previous step, $\bm{\nu}$ the reference value and $\bm{G(x_0)}$ the control effectiveness matrix. With $\bm{\Delta u=u-u_0}$ the control law from Equation \ref{eq:u_control_law_indi} represents an incremental version of the Equation \ref{eq:u_control_law}. This control law results in computing the increment $\bm{\Delta u}$ of the control input and adding it to the previous value $\bm{u_0}$, instead if computing complete control input command $\bm{u}$. As it is less dependent on the model of the system dynamics, it increases the robustness of the system \cite{Sieberling}.

>>>>

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% Compile Template in following order:
%
% pdflatex Paper_EV
% makeindex Paper_EV.nlo -s nomencl.ist -o Paper_EV.nls (Table of Symbols)
% makeindex Paper_EV.acn -s Paper_EV.ist -t Paper_EV.alg -o Paper_EV.acr (Table of Acronyms)
% makeindex Paper_EV.glo -s Paper_EV.ist -t Paper_EV.glg -o Paper_EV.gls
% pdflatex Paper_EV
% pdflatex Paper_EV
%
% TODO:
% - Title page: Dr. -> Dr. ir.
% - Acronyms, right order of full and short appearences
% - Create List of Symbols
%
%#################################################################################
%#################################################################################
%#################################################################################

@@

% Package for acronyms
\usepackage[acronym, automake, nopostdot, nogroupskip]{glossaries}
\setlength{\LTleft}{-0.15cm}			% left justified
\renewcommand*{\arraystretch}{1.4}		% vertical distance between entries, default is 1
% List
\newacronym{EOM}{EOM}{Equations of Motion}
\newacronym{INDI}{INDI}{Incremental Nonlinear Dynamic Inversion}
\newacronym{NED}{NED}{North East Down}
\newacronym{NDI}{NDI}{Nonlinear Dynamic Inversion}
% Make gls
\renewcommand*\entryname{Acronym}
\makeglossaries

@@

The aim of this chapter is to provide the theoretical background which serves as a basis for some of the methods which are presented and applied in the course of this thesis. At the beginning, in section \ref{sec:eqs_motion} general \acrfull{EOM} of an aircraft are presented. These are later used to derive the control algorithm and build the Matlab/Simulink model of the Crazyflie quadrotor. Sections \ref{sec:ndi} and \ref{sec:indi} describe the \acrfull{NDI} and \acrfull{INDI} methods in general. Later in this chapter (subsections \ref{subsec: indi_inner} and \ref{subsec: indi_outer}) these methods are used to derive the inner and the outer loop of the \acrshort{INDI} flight controller for the Crazyflie quadrotor.

@@

The dynamic equations which describe the general motion of an aircraft are usually coupled first order implicit nonlinear differential equations. However, in many cases it is sufficient to use their simplified versions (Source needed!). This section presents simplified general \acrshort{EOM} and describes the assumptions which were considered to derive them.

For the derivation of the equation of motion the aircraft system will be assumed to be a rigid body. Such a rigid body system can be described uniquely by 12 states. Note that by taking in account additional effects, such as propulsion system dynamics, multi-body dynamics etc., the number of required state variables will increase.

Additionally to the rigid body assumption, it is also assumed that the earth is flat and non-rotating and the reference point of the sum of all external forces acting on the body corresponds to the center of gravity of the body. Thus, the linear momentum equation is written as
\begin{equation}
	\begin{split}
		\sum (\bm{F}^G)_B = m \cdot \Big[ (\bm{\dot{v}}^G)_{B} + (\bm{\omega}^{OB})\times(\bm{v}^R)_{B} \Big]
		\label{eq:lin_momentum}
	\end{split}
\end{equation}
where $\sum(\bm{F}^G)_B \in \mathbb{R}^{3 \times 1}$ is the sum of the external forces acting on the system and applied to the center of gravity $G$, $m$ the mass of the body, $(\bm{\dot{v}}^G)_{B} \in \mathbb{R}^{3 \times 1}$ the linear acceleration of the point $G$, $(\bm{\omega}^{OB}) \in \mathbb{R}^{3 \times 1}$ the angular velocity of the body-fixed frame ($B$) with respect to the \acrfull{NED} ($O$) coordinate frame. Subscript $B$ denotes that all variables are specified in the body-fixed coordinate frame.

The rotational motion of a body is described with the angular momentum equation. To derive it, additionally to the assumptions made above it is also considered that the mass and the mass distribution are quasistationary, meaning $\frac{d}{dt}m=0$ and $\frac{d}{dt}(I)_B=0$ respectively?. $(I)_B$ is the inertia tensor of the body defined in the body-fixed frame. Thus, the angular momentum is
\begin{equation}
	\begin{split}
		\sum (\bm{M}^G)_B = (\bm{I}^G)_B \cdot (\bm{\dot{\omega}}^{OB}) + (\bm{\omega}^{OB}) \times \Big[(\bm{I}^G)_B \cdot (\bm{\omega}^{OB})\Big]
		\label{eq:ang_momentum}
	\end{split}
\end{equation}
where $\sum (\bm{M}^G)_B \in \mathbb{R}^{3 \times 1}$ is the sum of the external moments acting on the system around the center of gravity $G$.

The remaining two equations, that are necessary to fully describe the motion of a rigid body in space are the attitude differential equation and the position differential equation. The attitude differential equation describes the relationship between angular rates $p, q, r$ and derivatives of the Euler angles $\dot{\Phi}, \dot{\Theta}, \dot{\Psi}$ leading to
\begin{equation}
	\begin{bmatrix}
		\dot{\Phi}\\
		\dot{\Theta}\\
		\dot{\Psi}
	\end{bmatrix} =
	\begin{bmatrix}
    	1 & \sin\Phi\tan\Theta & \cos\Phi\tan\Theta \\
    	0 & \cos\Phi & -\sin\Phi \\
    	0 & \frac{\sin\Phi}{\cos\Theta} & \frac{\cos\Phi}{\cos\Theta}
    \end{bmatrix}_B
    \begin{bmatrix}
		p\\
		q\\
		r
	\end{bmatrix}_B
	\label{eq:attitude_diff_eq}
\end{equation}
where the angular rates are related to the derivatives of the Euler angles through the \textit{strapdown matrix}.

@@

The Equations (\ref{eq:lin_momentum})-(\ref{eq:position_diff_eq}) presented above can be used to represent a motion of a general aircraft. Note that terms $\sum(\bm{F}^G)_B$ and $\sum (\bm{M}^G)_B$ contain all external forces and moments acting on the rigid body. Considering an aircraft system these could be the aerodynamic forces and moments caused by the air flow, propulsion forces and moments, forces caused by the gravitation etc.. The detailed modelling of external forces and moments is presented in chapter (...Simulink).

@@

In this subsection, the \acrfull{NDI} method is explained. The \acrshort{NDI} approach is based on feedback linearization and is also called \textit{Input-Output Linearization}. Often, such type of controllers is involved in tracking control tasks, where objective is to track some desired trajectory \cite{Slotine}. To derive it, consider the following nonlinear system
\begin{subequations}
	\begin{align}
		&\bm{\dot{x}} = \bm{f(x)} + \bm{G(x)}\bm{u} \label{eq:nonlin_sys1} \\
		&\bm{y} = \bm{h(x)} \label{eq:nonlin_sys2}
	\end{align}
	\label{eq:nonlin_sys}
\end{subequations}
\hspace{-5pt}where $\bm{x} \in \mathbb{R}^{n \times 1}$ is the state vector, $\bm{u} \in \mathbb{R}^{m \times 1}$ the input vector, $\bm{y} \in \mathbb{R}^{m \times 1}$ the output vector, $\bm{f(x)} \in \mathbb{R}^{n \times 1}$ and $\bm{h(x) \in \mathbb{R}^{m \times 1}}$ nonlinear vector fields and $\bm{G} \in \mathbb{R}^{m \times n}$ an input matrix. Note that the system presented in Equations (\ref{eq:nonlin_sys}) is affine in the input, which is not allways fulfilled. Using a state transformation $\bm{z = \phi(x)}$, the affine system from Equation \ref{eq:nonlin_sys1} can be transformed into a \textit{normal} (\textit{canonical}) representation.

@@

In the example provided above the input-output relationsip was found after the first differentiation of the output $\bm{y}$. But if after the first differentiation the term $L_{\bm{G}}\bm{h(x)}$ is zero, output $\bm{y}$ has to be differentiated until the Lie derivative with respect to $\bm{G}$ is nonzero. The $i$-th derivative of the output is then
\begin{equation}
	\begin{split}
		\frac{\partial^i\bm{y}}{\partial t} = \frac{\partial^i\bm{h(x)}}{\partial t} = L_{\bm{f}}^i \bm{h(x)} + L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x) u}
		\label{eq:dy_i}
	\end{split}
\end{equation}
with $i$ being the \textit{relative degree} of the system. Using Equation (\ref{eq:dy_i}) to formulate the control law leads to the following expression for the control input $\bm{u}$
\begin{equation}
	\begin{split}
		\bm{u} = L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x)}^{-1} (\bm{\nu} - L_{\bm{f}}^i\bm{h(x)}) 
		\label{eq:u_control_law_i}
	\end{split}
\end{equation}
Thus, Equation (\ref{eq:u_control_law_i}) applied to Equation (\ref{eq:dy_i}) yields the simple linear relation
\begin{equation}
	\begin{split}
		\bm{y}^i = \bm{\nu}
		\label{eq:lin_relation}
	\end{split}
\end{equation}
The \acrshort{NDI} method was widely adopted for civil and military aircrafts and has numerous of extensions \cite{Horn}. Nevertheless, it has some drawbacks. The major one is that the control law derived using the \acrshort{NDI} approach is dependent on the full system dynamics model \cite{Sieberling}. The equations of motion of an aircraft usually have a complicated nonlinear character. Thus, describing complex physical phenomena often leads to the inconsistency between the real aircraft and its mathematical representation used in the model. As some of those inconsistencies are inevitable there is a need to build a control law which performance is less dependent on the uncertainties of the model. A method called \acrfull{INDI} can be used to achieve this, it is discussed in the next section.

@@

The incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
\begin{equation}
	\begin{split}
		\bm{\dot{x}} &= \bm{f(x_0)} + \bm{G(x_0)}\bm{u_0} \\
		&+ \frac{\partial}{\partial \bm{x}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{x-x_0}) \\
		&+ \frac{\partial}{\partial \bm{u}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{u-u_0}) 
		\label{eq:nonlin_sys_taylor}
	\end{split}
\end{equation}
The first term on the right side of the Equation \ref{eq:nonlin_sys_taylor} is $\bm{\dot{x}_0}$. Also, evaluating the differentiation of the third term leads to 
\begin{equation}
	\begin{split}
		\bm{\dot{x}} &= \bm{\dot{x}_0} \\ 
		&+ \frac{\partial}{\partial \bm{x}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{x-x_0}) \\
		&+ \bm{G(x_0)} (\bm{u-u_0}) 
		\label{eq:nonlin_sys_taylor2}
	\end{split}
\end{equation}
The second term of the Equation \ref{eq:nonlin_sys_taylor2} contains partial derivative with respect to the state vector. Considering very small time increments of the controller loop and applying the \textit{principle of time scale separation} the second term vanishes. This is a valid assumption if the dynamics of the actuators is fast compared with the dynamics of the system. Thus, the Equation \ref{eq:nonlin_sys_taylor2} is further simplified to 
\begin{equation}
	\begin{split}
		\bm{\dot{x}} = \bm{\dot{x}_0} + \bm{G(x_0)} (\bm{u-u_0}) 
		\label{eq:nonlin_sys_indi}
	\end{split}
\end{equation}
Solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\dot{\bm{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law is obtained
\begin{equation}
	\begin{split}
		\bm{u} = \bm{u_0} + \bm{G(x_0)^{-1}} (\bm{\nu} - \bm{\dot{x}_0})
		\label{eq:u_control_law_indi}
	\end{split}
\end{equation}
where $\bm{\dot{x}_0}$ is a measurable value from the previous step, $\bm{u_0}$ the control input from the previous step, $\bm{\nu}$ the reference value and $\bm{G(x_0)}$ the control effectiveness matrix. With $\bm{\Delta u=u-u_0}$ the control law from Equation \ref{eq:u_control_law_indi} represents an incremental version of the Equation \ref{eq:u_control_law}. Instead of computing the complete control input command $\bm{u}$, this control law results in computing the increment of the control input $\bm{\Delta u}$ and adding it to the previous value $\bm{u_0}$. As it is less dependent on the model of the system dynamics, it is able to increase the robustness of the system \cite{Sieberling}.
